### 2015-10-07 postdoctoral/S_prime_kappa.tex
proof for omega_2

  \begin{theorem}
    There exists a topology on \(\omega_2\) which
    is \(\omega\)-bounded, locally compact, and locally countable.
  \end{theorem}

@@

    We wish to show that \(\omega_2\) with the topology induced by
    \(\bigcup_{\alpha<\omega_2}\omega_1\cdot(\alpha+1)\) is \(\omega\)-bounded,
    locally compact, and locally countable. If
    \(\gamma\in\omega_1\cdot(\alpha+1)\setminus\omega_1\cdot\alpha\) where
    \(cf(\alpha)\not=\omega\), then we immediately see that it is in a clopen
    copy of \(\omega_1\) giving us local compactness and local countability
    immediately. Otherwise, \(\gamma\) has a basic open neighborhood of the form
    \(
      [\gamma',\gamma]
        \cup
      f_\alpha[[\omega_1\cdot\alpha,\gamma]]
        \setminus
      \omega_1\cdot(\alpha_n+1)
    \),
    which is obviously countable. Likewise, its closure is compact:
    the closure operation does not add any ordinals greater than \(\gamma\),
    and any open cover
    contains another basic open neighborhood of \(\gamma\) such as
    \(
      [\gamma'',\gamma]
        \cup
      f_\alpha[[\omega_1\cdot\alpha,\gamma]]
        \setminus
      \omega_1\cdot(\alpha_m+1)
    \)
    which misses only the compact set \([\gamma',\gamma'']\) and the
    closure of the countable set
    \(
      f_\alpha[[\omega_1\cdot\alpha,\gamma]]
        \cap
      \omega_1\cdot(\alpha_{\min(m,n)}+1)
    \), which will be proven to be compact once we show that
    \(\omega_1\cdot(\alpha+1)\) is \(\omega\)-bounded for all
    \(\alpha<\omega_2\). This also will show that \(\omega_2\) with our
    topology is itself \(\omega\)-compact, finishing the proof.

  \end{proof}

  \begin{theorem*}
    \(S'(\omega_\omega)\).
  \end{theorem*}

>>>>

  \begin{theorem}
    There exists a topology on \(\omega_2\) which
    is \(\omega\)-bounded and locally countable.
  \end{theorem}

@@

    We wish to show that \(\omega_2\) with the topology induced by
    \(\bigcup_{\alpha<\omega_2}\omega_1\cdot(\alpha+1)\) is \(\omega\)-bounded
    and locally countable. If
    \(\gamma\in\omega_1\cdot(\alpha+1)\setminus\omega_1\cdot\alpha\) where
    \(cf(\alpha)\not=\omega\), then we immediately see that it is in a clopen
    copy of \(\omega_1\) giving us local countability
    immediately. Otherwise, \(\gamma\) has a basic open neighborhood of the form
    \(
      [\gamma',\gamma]
        \cup
      f_\alpha[[\omega_1\cdot\alpha,\gamma]]
        \setminus
      \omega_1\cdot(\alpha_n+1)
    \),
    which is obviously countable.

    Let \(C\) be a countable subset of \(\omega_1\cdot(\alpha+1)\).
    In the case that \(\alpha=\beta+1\), we may use the \(\omega\)-boundedness
    of each part in the clopen partition \(\omega_1\cdot(\beta+1)\) and
    \(\omega_1\cdot(\beta+2)\setminus\omega_1\cdot(\beta+1)\cong\omega_1\)
    to conclude that the closure of \(C\) is compact.
    Similarly, if \(cf(\alpha)>\omega\),
    then we may use the  \(\omega\)-boundedness
    of each part in the clopen partition
    \(\bigcup_{\beta<\alpha}\omega_1\cdot(\beta+1)\) and
    \(\omega_1\cdot(\alpha+1)\setminus\omega_1\cdot\alpha\cong\omega_1\)
    to conclude that the closure of \(C\) is compact.

    The remaining case is again where \(\alpha\) is the limit of increasing
    \(\alpha_n\) for \(n<\omega\). Then
    \(
      C
        \subseteq
      [\gamma',\gamma]
        \cup
      f_\alpha[[\omega_1\cdot\alpha,\gamma]]
    \)
    for some \(\omega_1\cdot\alpha\leq\gamma'<\gamma<\omega_1\cdot(\alpha+1)\).
    Its closure is compact:
    the closure operation does not add any ordinals greater than \(\gamma\),
    and any open cover
    contains another basic open neighborhood of \(\gamma\) such as
    \(
      [\gamma'',\gamma]
        \cup
      f_\alpha[[\omega_1\cdot\alpha,\gamma]]
        \setminus
      \omega_1\cdot(\alpha_m+1)
    \)
    which misses only the compact set \([\gamma',\gamma'']\) and the
    closure of the countable set
    \(
      f_\alpha[[\omega_1\cdot\alpha,\gamma]]
        \cap
      \omega_1\cdot(\alpha_{\min(m,n)}+1)
    \), which is compact by the \(\omega\)-boundedness of
    \(\omega_1\cdot(\alpha_{\min(m,n)}+1)\).

    Finally, since every countable subset of \(\omega_2\) is contained in
    some \(\omega_1\cdot(\alpha+1)\), we conclude \(\omega_2\) is
    \(\omega\)-bounded.
  \end{proof}

  \begin{theorem*}
    \(S'(\omega_2)\).
  \end{theorem*}
